### 2024-11-07 README.Rmd
printing + formatting for embeddings objects
plus a few other embeddings methods

>>>>

## Functionality

embeddingplyr is designed to facilitate the use of word and text embeddings in common data manipulation and text analysis workflows, without introducing new syntax or unfamiliar data structures.

embeddingplyr is model agnostic; it can be used to work with embeddings from decontextualized models like [GloVe](https://nlp.stanford.edu/projects/glove/) and [word2vec](https://code.google.com/archive/p/word2vec/), or from contextualized models like BERT or others made available through the [text](https://r-text.org) package.

### Loading Pretrained Embeddings

embeddingplyr won't help you train new embedding models, but it can load embeddings from a file. This is especially useful for pretrained word embedding models like GloVe and word2vec. These models can be downloaded (generally in txt or bin format, respectively) and loaded with `load_embeddings()`.

```{r, warning=FALSE, message=FALSE}
library(embeddingplyr)

glove_twitter_25d <- load_embeddings("~/Documents/data/glove/glove.twitter.27B.25d.txt")
```

The outcome is an "embeddings" object. An embeddings object is just a numeric matrix with tokens as rownames. This means that it can be easily coerced to a dataframe or tibble, while also allowing special embeddings-specific methods and functions, such as `predict.embeddings()` and `find_nearest()`:

```{r}
moral_embeddings <- predict(glove_twitter_25d, c("good", "bad"))
moral_embeddings

find_nearest(glove_twitter_25d, "dog", 5L)
```

### Similarity Metrics

### Tidy Workflow

### Quanteda Workflow
